Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-10-28 cbm-rbd-paper.tex
typo in 5.2., some clarification in 5.3
minor thing

Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
such a fine discrete approximation of the RLD can be obtained.

\section{Dynamic/Adaptive maintenance policy based on the current system residual life distribution}
\label{sec:policy}

@@

>>>>

Next, we will describe how an adaptive maintenance policy based on %\eqref{eq:sysrel-tnow}
a current residual life distribution,
first in general, then for our implementation,
where a fine discrete approximation of the RLD is obtained.

\section{Dynamic and adaptive maintenance policy based on the current system residual life distribution}
\label{sec:policy}

@@

***comments about `nervousness' of $\tausnow$ here or in \ref{sec:operationalprocedure}?
